Cognitive Principles and Individual Differences \\ in Human Syllogistic Reasoning

### 2019-11-18 paper/paper-v3.tex
small change first paragraph

Even though the main logical formalism of Classical Logic (CL) has successfully been applied to our scientific reasoning,
it seems that already in 1913, Kotarbi{\'n}ski~\cite{kotarbinski:1913} \textit{suggested
the need to revise the two-valued logic as it seemed to interfere with the freedom of human thinking}~\cite[p.17]{malinowski:1993}.
% Originally, one of the objectives in the field of AI and logic programming was to formalize human reasoning and commonsense reasoning~\cite{McCarthy59,McCarthy98}. 
% However, the proposed approaches have been strongly critized~(cf.~\cite{mcdermott:87}).
% On the other hand, cognitive scientists have extensively investigated and acquired a great expertise
% in human thinking. Recently, several attempts have been made to bridge the gap among these disciplines. 
% % as they were mostly theoretical and did not apply to real case studies.
% However, only recently an attempt was made 
% this expertise was not consulted, i.e. there was no communication among the relevant fields. 
Since then, various cognitive theories have been proposed,
 but it seems that none of them is generally accepted
within the community. As various experimental studies have shown that human reasoning systematically deviates from conclusions that are valid under CL (cf.~\cite{wason:68,byrne:89}),
cognitive scientists 
seem at least to agree with Kotarbi{\'n}ski,
 that classical (two-valued)
logic would not be an adequate candidate for a cognitive theory.

>>>>

Even though the main logical formalism of Classical Logic (CL) has successfully been applied to our scientific reasoning,
it seems that already in 1913, Kotarbi{\'n}ski~\cite{kotarbinski:1913} \textit{suggested
the need to revise the two-valued logic as it seemed to interfere with the freedom of human thinking}~\cite[p.17]{malinowski:1993}.
% Originally, one of the objectives in the field of AI and logic programming was to formalize human reasoning and commonsense reasoning~\cite{McCarthy59,McCarthy98}. 
% However, the proposed approaches have been strongly critized~(cf.~\cite{mcdermott:87}).
% On the other hand, cognitive scientists have extensively investigated and acquired a great expertise
% in human thinking. Recently, several attempts have been made to bridge the gap among these disciplines. 
% % as they were mostly theoretical and did not apply to real case studies.
% However, only recently an attempt was made 
% this expertise was not consulted, i.e. there was no communication among the relevant fields. 
% but providing a unified, integrated  accepted theory still appears 
% to be a major challenge. 
In the last decades, cognitive scientists have repeatedly
shown through experimental studies that human reasoning systematically deviates from conclusions that are valid under CL (cf.~\cite{wason:68,byrne:89}),
and thus it seems that they agree with Kotarbi{\'n}ski,
 that classical (two-valued) logic would not be an adequate candidate for a cognitive theory.
